### 2022-11-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter6): Save point

      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} presents discussions on heuristic-entity selections.

      \item \textbf{Section \ref{sec:bhh:model}} presents the models that can be optimised using the \Acs{BHH}, specifically referring to the training of \acp{FFNN}.

      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} presents a brief discussion on the role of datasets for training and testing.

      \item \textbf{Section \ref{sec:bhh:loss_function}} presents discussions on model evaluation and the role of the loss function.

      \item \textbf{Section \ref{sec:bhh:domain_barrier}} presents discussions on the domain barrier, an information barrier that exists between the high-level \acs{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.

@@

      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy.

@@

      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \ac{BHH}.

@@

\begin{itemize}
      \item \textbf{Population-Based:} The \ac{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.

      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \ac{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself. Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.

@@

Another design decision in the heuristic pool is heuristic pool size. Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance. Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining \textit{state}. State is the term used to describe data that is relevant to the training process, and is maintained between training steps. An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far. The following section presents the concept of \textit{proxies} and their role in maintaining state.

@@

\noindent
Primary and proxied state parameters must be maintained together. Since entities represent candidate solutions, which are forms of state, entities are ideal candidates to store and maintain these state parameters. Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}. At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method. The \ac{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.

@@

Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}. It can be said that entities implement \textit{local} state. It was mentioned that these entities can be treated as physical \index{particle}\textit{particles} in a hyper-dimensional search environment. Entities model concepts from physics. For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully. Examples of \index{Entity State}entity state parameters, as derived from various low-level heuristics, is given as follows.

\begin{itemize}
      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all heuristics.

      \item \textbf{velocity}: Directly implemented by heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based heuristics such as \ac{Momentum}.

      \item \textbf{gradient}: The last known gradient, as derived from gradient-based heuristics.

@@

      \item \textbf{sum of the gradients squared}: As required and maintained by heuristics such as \acs{Adagrad}.

      \item \textbf{expected position delta variance}: As required and maintained by heuristics such as \acs{Adadelta}.

      \item \textbf{expected gradient mean}: As required and maintained by heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.

      \item \textbf{expected gradient variance}: As required and maintained by heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.

      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.

      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.

@@

\noindent
From the list above, it should be clear that entity state becomes increasingly complicated as the number of distinct \index{heuristic}heuristics, included in the \index{heuristic pool}heuristic pool, increases.

@@

The population state refers to a collection of parameters that are shared between the entities in the population. Population state is also referred to as \textit{global} state and represents the population's memory. The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual heuristic. Some examples of population state that can arise from different \index{heuristic}heuristics is given below:

@@

      \item \textbf{ibest} and \textbf{ibest loss}: Refers to the best position and loss achieved by the population for the current iteration/step. This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{ibest} credit assignment strategy.

      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size. This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{rbest} credit assignment strategy.

      \item \textbf{gbest} and \textbf{gbest loss}: Refers to the overall/global best position and loss achieved by the population for the entire training process. This parameter is introduced by heuristics such as \acp{PSO}, and is also introduced by the \ac{BHH} itself through the requirements of the \textit{gbest} credit assignment strategy.
\end{itemize}

\noindent
Entities in the entity pool are each assigned an associated \index{heuristic}heuristic. The following section provides details around the heuristic-entity selection process.

\section{Heuristic-Entity Selections}
\label{sec:bhh:heuristic_entity_selections}

The \ac{BHH} selects from the \index{heuristic pool}heuristic pool a low-level heuristic to be applied to an entity. The outcome of this selection process is a table that tracks which heuristic has been selected for which entity. The selection process is executed by the selection mechanism of the \ac{BHH} and is discussed later in Section \ref{sec:bhh:selection_mechanism}. These heuristic-entity combinations are applied to an underlying model. The next section provides clarity on the model component from the architecture of the \ac{BHH}.

\index{Model}
\section{Model}
\label{sec:bhh:model}

The \index{Model}model refers to the target model to be optimised and is usually expressed as a complex mathematical function. For this dissertation, the authors focused specifically on shallow \acp{FFNN} (only one hidden layer). Figure \ref{fig:shallow_ffnn} below presents such a shallow \acp{FFNN}.

\begin{figure}[htbp]
      \centering
      \includegraphics[width=0.4\textwidth]{shallow_ffnn.pdf}
      \caption[Shallow \index{Feedforward Neural Network}Feedforward Neural Network]{An illustration of
            a shallow \index{Feedforward Neural Network}Feedforward Neural Network.}
      \label{fig:shallow_ffnn}
\end{figure}

\section{Train and Test Datasets}
\label{sec:bhh:train_test_datasets}

The training of \ac{FFNN} is a supervised learning problem as was highlighted in Chapter \ref{chap:anns}. Therefore, the \ac{BHH} trains the model on training data from the training set, while is reserves an unseen set of test data in the test dataset for evaluation. It should be mentioned that the goal of the \ac{BHH} is to generalise well to the test set across a number of problem domains. As was previously mentioned, the test set should be sufficiently large to truly evaluate for generalisation capabilities. For the \ac{BHH}, it is proposed to have a 80-20\% split between the training and test set.

\section{Loss/Cost Function}
\label{sec:bhh:loss_function}

Chapter \ref{chap:anns} presented the concept of a loss/cost function that is used to evaluate the performance of \acp{ANN}. The \ac{BHH} uses this loss/cost function to evaluate the performance of a heuristic-entity combination. For classification problems, generally some entropy loss is used. For classification problems with 2 classes, \ac{BinXE} is used and for classification problems with more than 2 classes, the \ac{SparseCatXE} is used. For regression problems it is recommended to use some mean error measurement such as \ac{MSE} or \ac{RMSE}.

The loss/cost function is very important as this metric is used to evaluate model performance as a result of the application of a heuristic to an entity's candidate solution. The \ac{BHH} used this performance metric to bias towards good heuristic-entity combinations.  The continuous valued cost/loss function is translated into a discrete valued representation through a credit assignment strategy that is implemented in the \ac{BHH}. The credit assignment strategies is discussed in Section \ref{sec:bhh:credit_assignment_strategy}.

\section{Domain Barrier}
\label{sec:bhh:domain_barrier}

The domain barrier presents the boundary of information flow between the heuristic space and the solution space. It is mentioned in Section \ref{sec:bhh:loss_function} that the heuristic-entity loss is used by the \ac{BHH}. Notice that the \ac{BHH} uses this performance information and no information from the solution space itself. Furthermore, the \ac{BHH} maps this loss to a credit assignment problem as is mentioned by Burke et al.~\cite{ref:burke:2010}. The \ac{BHH} at a high level, is not aware of the actual candidate solution that is represented by the entity, but rather just that there is a candidate solution with a unique identifier that, together with a heuristic, produced a certain level of performance. The domain barrier is a feature that occurs in al \acp{HH}.  Burke et al.~\cite{ref:burke:2010} states that the \ac{HH} collects domain-independent information from the domain barrier. A number of examples of domain independent information is given, these include the number of heuristics, the changes in evaluation function, whether a new solution was found or generated, the distance between two solutions, whether it has become stuck.

\index{Performance Log}
\section{Performance Log}
\label{sec:bhh:performance_log}

Recall that the \ac{BHH} incorporates a Bayesian probabilistic implementation. Evidence is required to train the \ac{BHH}. The performance log is used to keep memory of a slice of the performance history. The performance log is simply a tabular implementation that tracks random events. The \ac{BHH} suggests the following metrics to keep track of in the performance log:

@@

      \item \textbf{heuristic}: The selected heuristics' index.

      \item \textbf{entity}: The applied entity's index.

      \item \textbf{loss}: The heuristic-entity performance metric.

      \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations for a single mini-batch step.

      \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps currently in the performance log.

      \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps thus far.
\end{itemize}

The performance log as implemented by the \ac{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.

\begin{table}[htbp]
      \centering
      \caption{Performance log example showing the first 5 entity's selected heuristics for step 1 and their resulting performance measurements.}
      \label{tab:bhh:performance_log:performance_log_example}%
      \par\bigskip
      \resizebox{\textwidth}{!}{
            \begin{tabular}{cccccccc}
                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest Loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
                  \midrule
                  1             & 1               & 1                  & 0.016444      & 0.016444            & 0.016444            & 0.016444            & 0.016444            \\
                  1             & 2               & 2                  & 0.337965      & 0.016444            & 0.337965            & 0.016444            & 0.016444            \\
                  1             & 3               & 1                  & 0.134781      & 0.016444            & 0.134781            & 0.016444            & 0.016444            \\
                  1             & 4               & 1                  & 0.998719      & 0.016444            & 0.998719            & 0.016444            & 0.016444            \\
                  1             & 5               & 3                  & 0.708702      & 0.016444            & 0.708702            & 0.016444            & 0.016444            \\
            \end{tabular}%
      }
\end{table}%

The performance log itself introduces a number of design considerations as well. Since the log contains a slice of memory, there should exists a trade-off between the following parameters:

\begin{itemize}
      \item \textbf{performance log size}: The larger the performance log, the longer memory is retained.The performance log size controls the recency of evidence from which new beliefs must be derived. This parameter is called the \textit{replay} window size, a term borrowed from \ac{RL} and should be empirically tested. If the replay window size is too small, it does not accumulate enough samples/evidence to really statistically make accurate classifications. If the replay window size is too back, the \ac{BHH} might remember too much of past performance and it could be that past performance is not indicative of future performance during the training process. Notice then that the performance log must be pruned to maintain a fixed replay window size. Dynamic replay window sizes is left as a research component for the future.

      \item \textbf{performance log reanalysis}: Consider the temporal nature of the performance log. Since it tracks all random events across all steps in the training process, it is needed to reanalyse the performance log appropriately in order to update the past information in the performance log with newly added data. An example of this is when a new rbest value has been found. Then the entire performance log's rbest loss must be updated.
\end{itemize}

The performance log should be considered along with the selection of credit assignment strategy used. These are discussed next.

\index{Credit Assignment Strategy}
\section{Credit Assignment Strategy}
\label{sec:bhh:credit_assignment_strategy}

The credit assignment strategy is an implementation that maps a continuous performance metric into a discrete credit metric. This component implements the ``move acceptance'' process as proposed by Özcan et al.~\cite{ref:ozcan:2006,ref:ozcan:2008}. It determines if a given performance is deemed good or not. This simple discrete transformation is subject to the credit assignment problem as discussed by Burke et al.~\cite{ref:burke:2010}. A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination. THe magnitude of this credit is to be empirically tested.  It is later shown how these credit metrics are used to accumulate ``pseudo counts'' which concentrates/biases heuristic selection towards good performing heuristics. The \ac{BHH} propose the following initial credit assignment strategies.

\begin{itemize}
      \item \textbf{ibest}: Credit is assigned to the heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current mini-batch iteration.

      \item \textbf{pbest}: Credit is assigned to the heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-heuristic combination that was able to improve on it's personal best past performance loss.

      \item \textbf{rbest}: Credit is assigned to the heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current replay window.

      \item \textbf{gbest}: Credit is assigned to the heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-heuristic combination that achieved the overall best performance so far.

      \item \textbf{symmetric}: A credit assignment strategy that gives credit to all entity-heuristic combinations regardless of performance. This credit assignment strategy suggests that ``symmetric'' credit assignment be given. As a result, any bias that arise from uncertainty or as a result of an untrained \ac{BHH} model, in the beginning, is maintained and further strengthened throughout the training process . Notice that this credit assignment strategy does not randomly assign credit, it simply assigns credit to the all events that are a result of random selection, which could be possibly be biased.
\end{itemize}

The implementation of a credit assignment strategy is a pure, stateless function that translates input $P$ from the performance log into output $C$ as is given in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.

\begin{table}[htbp]
      \centering
      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entity's and their selected heuristics for step 1 of the training process.}
      \label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
      \par\bigskip
      \resizebox{0.4\textwidth}{!}{
            \begin{tabular}{cccc}
                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{credit} \\
                  \midrule
                  1             & 1               & 1                  & true            \\
                  1             & 2               & 2                  & false           \\
                  1             & 3               & 1                  & false           \\
                  1             & 4               & 1                  & false           \\
                  1             & 5               & 3                  & false           \\
            \end{tabular}%
      }
\end{table}%

Credit assignment is a key component of the \ac{BHH} is it will later be shown in Section \ref{sec:bhh:optimisation_step} how these credit assignments are used to optimise the \ac{BHH}. First, it is necessary to present the selection mechanism.

\index{Selection Mechanism}
\section{Selection Mechanism}
\label{sec:bhh:selection_mechanism}

This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \ac{BHH}. It is mentioned throughout this document that the \ac{BHH} implements a predictive model based on Bayesian probabilistic concepts. In probabilistic modeling it is necessary to identify all the random events that can occur.

\index{Random Events}
\subsection{Random Events}
\label{sec:bhh:selection_mechanism:random_events}

Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \ac{BHH} distinguishes between the following events:

\begin{itemize}
      \item \textbf{$H$}: The event of observing \textit{heuristics}.
      \item \textbf{$E$}: The event of observing \textit{entities}.
      \item \textbf{$C$}: The event of observing \textit{credit assignments}.
\end{itemize}

It should be noted that this information is observed direclty from the performance log presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} above. From the above list, the event $C$ is dependent on the occurrence of $H$ and $E$. However, for simplification, an argument for independence can be made.

\index{Independence}
\subsection{Independence}
\label{sec:bhh:selection_mechanism:independence}

The dependence between random events can have a drastic impact on the probabilistic model that is implemented. For simplicity, the \ac{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$. Notice that the \ac{BHH} is fundamentally a classifier, classifying which heuristic to select given an entity and performance criteria. It is later shown in Section \ref{sec:bhh:selection_mechanism:naive_bayes} that the \ac{BHH} implements a Naïve Bayes classifier. Domingos et al.~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can be optimal under zero-one loss (misclassification rate) even when this assumption is violated by a wide margin. This means that independence can be assumed when the probabilistic model is used as a classifier and not to get real probabilities. Evaluating for proportionality and not precision allows for the assumption of independence.

\index{Bayes' Theorem}
\subsection{Bayes' Theorem}
\label{sec:bhh:selection_mechanism:bayes_theorem}

Section \ref{sec:bhh:selection_mechanism:random_events} presented the reader with the random events that are observed by the \ac{BHH} and Section \ref{sec:bhh:selection_mechanism:independence} provided an argument for independence between events. Chapter \ref{chap:probability} presented Bayes Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.

@@

As was indicated in Section \ref{sec:bhh:selection_mechanism:independence}, Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality since the \ac{BHH} is not concerned with actual accurate selection probabilities, but rather implements a Bayesian classifier. The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below

@@

Notice how the Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} implements a Bayesian conditionally. This conditionality can be extended to include multiple criteria. The next section shows how the Bayesian classifier is implemented by providing the detail around the implemented predictive model.

\subsection{Predictive Model}
\label{sec:bhh:selection_mechanism:predictive_model}

Finally the reader is presented with the underlying predictive model as implemented by the \ac{BHH}. This component is arguably the most important component of the entire \ac{BHH} as it fundamentally drives the output of the \ac{BHH}. Bayes Theorem as was shown again in Section \ref{sec:bhh:selection_mechanism:bayes_theorem} above can be used to implement a predictive model to predict which heuristic to select, given the conditionality of a particular entity and a particular credit assignment criteria is met. Consider the following setup. Let

@@

            \State apply low-level heuristic and proxy operations
            \State update population state
            \State log performance to performance log

>>>>

@@

@@

      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \acs{BHH}.

@@

\begin{itemize}
      \item \textbf{Population-Based:} The \acs{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.

      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself. Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.

@@

Another design decision in the heuristic pool is heuristic pool size. Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance. Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \acs{BHH}, but it also drastically complicates the process of maintaining \textit{state}. State is the term used to describe data that is relevant to the training process, and is maintained between training steps. An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far. The following section presents the concept of \textit{proxies} and their role in maintaining state.

@@

\noindent
Primary and proxied state parameters must be maintained together. Since entities represent candidate solutions, which are forms of state, entities are ideal candidates to store and maintain these state parameters. Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}. At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method. The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.

@@

Entities represent candidate solutions to the model's trainable parameters (weights) and other \index{heuristic}heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}. It can be said that entities implement \textit{local} state. It was mentioned that these entities can be treated as physical \textit{particles} in a hyper-dimensional search environment. Entities model concepts from physics. For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully. Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows.

\begin{itemize}
      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all \index{heuristic}heuristics.

      \item \textbf{velocity}: Directly implemented by \index{heuristic}heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based \index{heuristic}heuristics such as \ac{Momentum}.

      \item \textbf{gradient}: The last known gradient, as derived from gradient-based \index{heuristic}heuristics.

@@

      \item \textbf{sum of the gradients squared}: As required and maintained by \index{heuristic}heuristics such as \acs{Adagrad}.

      \item \textbf{expected position delta variance}: As required and maintained by \index{heuristic}heuristics such as \acs{Adadelta}.

      \item \textbf{expected gradient mean}: As required and maintained by \index{heuristic}heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.

      \item \textbf{expected gradient variance}: As required and maintained by \index{heuristic}heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.

      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.

      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.

@@

\noindent
From the list above, it should be clear that entity state becomes increasingly complicated with the increase of the number of distinct \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool with unique state parameters.

@@

The population state refers to a collection of parameters that are shared between the entities in the population. Population state is also referred to as \textit{global} state and represents the population's memory. The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual \index{heuristic}heuristic. Some examples of population state that can arise from different \index{heuristic}heuristics is given below.

@@

      \item \textbf{ibest} and \textbf{ibest loss}: Refers to the best position and loss achieved by the population for the current iteration/step.

      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.

      \item \textbf{gbest} and \textbf{gbest loss}: Refers to the overall/global best position and loss achieved by the population for the entire training process. This parameter is introduced by \index{heuristic}heuristics such as \acp{PSO}.
\end{itemize}

\noindent
Entities in the entity pool are each assigned an associated \index{heuristic}heuristic. The \acs{BHH} selects from the \index{heuristic pool}heuristic pool a low-level \index{heuristic}heuristic to be applied to an individual entity. The outcome of this selection process is a mapping table that tracks which \index{heuristic}heuristic has been selected for which entity. The selection process is executed by the selection mechanism of the \acs{BHH}. These \index{heuristic}heuristic-entity combinations are applied to the underlying \acs{FFNN}. The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log. The performance log is presented in the following section.

\section{Performance Log}\label{sec:bhh:performance_log}

The \acs{BHH} incorporates a form of probabilistic modeling in its selection mechanism. Probability is calculated based on \index{heuristic}heuristic-entity performance over time. Evidence of \index{heuristic}heuristic-entity performance is thus required for the \acs{BHH} to learn. Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process. The sliding window is also referred to as a \textit{replay} buffer, a term borrowed from the field of \acf{RL}. The replay window size is defined as a hyper-parameter of the \acs{BHH}. The performance log is then simply a table of events and metrics. The \acs{BHH} tracks the following metrics in the performance log.

@@

      \item \textbf{\index{heuristic}heuristic}: The selected heuristic's index.

      \item \textbf{entity}: The entity's index to whom the \index{heuristic}heuristic is applied.

      \item \textbf{loss}: The \index{heuristic}heuristic-entity performance metric. The loss is retrieved from the loss function.

      \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss. Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, for a single mini-batch step.

      \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss. Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, over all mini-batch steps currently in the performance log/replay buffer.

      \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss. Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations over all mini-batch steps thus far.
\end{itemize}

\noindent
An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.

\begin{table}[htbp]
      \centering
      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first 5 entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
      \label{tab:bhh:performance_log:performance_log_example}%
      \par\bigskip
      \resizebox{\textwidth}{!}{
            \begin{tabular}{cccccccc}
                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
                  \midrule
                  1             & 1               & 1                  & 0.016444      & 0.016444            & 0.016444            & 0.016444            & 0.016444            \\
                  1             & 2               & 2                  & 0.337965      & 0.016444            & 0.337965            & 0.016444            & 0.016444            \\
                  1             & 3               & 1                  & 0.134781      & 0.016444            & 0.134781            & 0.016444            & 0.016444            \\
                  1             & 4               & 1                  & 0.998719      & 0.016444            & 0.998719            & 0.016444            & 0.016444            \\
                  1             & 5               & 3                  & 0.708702      & 0.016444            & 0.708702            & 0.016444            & 0.016444            \\
            \end{tabular}%
      }
\end{table}%

\noindent
The performance log itself introduces a number of design considerations as well. The larger the performance log, the longer memory is retained throughout the training process. The performance log size, referred to as the \textit{replay window size}, controls the recency of evidence from which the \acs{BHH} must learn. If the replay window size is too small, it does not accumulate enough samples/evidence to statistically make accurate selections. If the replay window size is too big, a bias could exist for selecting \index{heuristic}heuristics that performed well in the past. Furthermore, it is not guaranteed that past performance is indicative of future performance during the training process. The performance log should be considered along with the selection of a credit assignment strategy. Credit assignment strategies are presented in the following section.

\section{Credit Assignment Strategy}
\label{sec:bhh:credit_assignment_strategy}

The credit assignment strategy is a mechanism that assigns a discrete credit indicator to \index{heuristic}heuristics that perform well, based on their performance metrics such as loss. The credit assignment strategy implements the ``move acceptance'' process as proposed by~\citeauthor{ref:ozcan:2006}~\cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}. A good credit assignment strategy will correctly allocate credit to the appropriate \index{heuristic}heuristic-entity combination. The credit assignment strategy to use is defined as a hyper-parameter. The \acs{BHH} implements the following credit assignment strategies to choose from.

\begin{itemize}
      \item \textbf{ibest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current mini-batch iteration.

      \item \textbf{pbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that was able to improve on its personal best past performance loss.

      \item \textbf{rbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current replay window.

      \item \textbf{gbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the overall best performance so far.

      \item \textbf{symmetric}: Credit is assigned to all entity-\index{heuristic}heuristic combinations, regardless of their performance. The symmetric credit assignment strategy does not randomly assign credit, but rather assigns credit to all events. In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus, the symmetric credit assignment strategy is implemented as a basis for comparison. Comparing a credit assignment staretegy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
\end{itemize}

\noindent
The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.

\begin{table}[htbp]
      \centering
      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entities and their selected heuristics, for step 1 of the training process.}
      \label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
      \par\bigskip
      \resizebox{0.4\textwidth}{!}{
            \begin{tabular}{cccc}
                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{credit} \\
                  \midrule
                  1             & 1               & 1                  & true            \\
                  1             & 2               & 2                  & false           \\
                  1             & 3               & 1                  & false           \\
                  1             & 4               & 1                  & false           \\
                  1             & 5               & 3                  & false           \\
            \end{tabular}%
      }
\end{table}%

\noindent
Credit is used by the selection mechanism of the \acs{BHH}. The selection mechanism is presented in the following section.

\section{Selection Mechanism}\label{sec:bhh:selection_mechanism}

This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \acs{BHH}. It is mentioned throughout this document that the \acs{BHH} implements a predictive model based on Bayesian probabilistic concepts. In probabilistic modeling it is necessary to identify all the random events that can occur.

\subsection{Random Events}
\label{sec:bhh:selection_mechanism:random_events}

Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \acs{BHH} distinguishes between the following events.

\begin{itemize}
      \item \textbf{$H$}: The event of observing \textit{heuristics}.
      \item \textbf{$E$}: The event of observing \textit{entities}.
      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} is met.
\end{itemize}

\noindent
It should be noted that event information is stored and observed direclty from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}. From the above list of events, the event $C$ is dependent on the occurrence of $H$ and $E$ and a credit assignment strategy.

\subsection{Independence}\label{sec:bhh:selection_mechanism:independence}

The dependence between random events can have an impact on the probabilistic model that is implemented. For simplicity, the \acs{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$. Furthermore, the \acs{BHH} assumes independence between steps  and treats each training step as if training has restarted. The \acs{BHH} implements a form of Naïve Bayes classifier, where the appropriate heuristic to assign to an entity is a classification problem. \citeauthor{ref:domingos:1997}~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can still be optimal under zero-one loss (misclassification rate), even when this assumption is violated by a wide margin. This means that independence can be assumed when the probabilistic model is used as a classifier.

\index{Bayes' Theorem}
\subsection{Bayes' Theorem}\label{sec:bhh:selection_mechanism:bayes_theorem}

Chapter \ref{chap:probability} presented \index{Bayes' Theorem}Bayes' Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.

@@

\noindent
Since the \acs{BHH} implements a Bayesian classifier, the \acs{BHH} is not concerned with actual probabilities. Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can thus be evaluated for proportionality. The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below.

@@

\noindent
The conditionality implemented by \index{Bayes' Theorem}Bayes' Theorem can be extended to include multiple criteria. \index{Bayes' Theorem}Bayes' Theorem is used by the selection mechanism of the \acs{BHH}. The predictive model that is used by the selection mechanism of the \acs{BHH} is presented in the following section.

\subsection{Predictive Model}\label{sec:bhh:selection_mechanism:predictive_model}

This section presents the predictive model as implemented by the selection mechanism of the \acs{BHH}. The predictive model is arguably the most important component of the \acs{BHH}, as it drives heuristic selection process. The \acs{BHH} implements a predictive model that predicts which heuristic to select, given the conditionality that a particular entity is used and a particular credit assignment criteria is met. The predictive model can be derived as follows.\\\\
\textbf{Setup}:
\\
\noindent
Let

@@

            \State apply low-level heuristic and proxy operations
            \State update population state
            \State log performance metrics to performance log
